%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{EXPERIENCE}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries2}

%---------------------------------------------------------
  \cventrynew
    {Outlier AI, \textnormal{\textit{Coding \& Math Expert / AI Trainer} | Remote (Contractor)}} % Job title
    {Dec 2024 – Present} % Date(s)
    {
      \begin{cvitems}
        \item {Authored and reviewed math and coding problems, validating AI-generated solutions for correctness and clarity.}
        \item {Reviewed AI-generated code for correctness, efficiency, and style across Python, C++, and JavaScript.}
        \item {Generated and ranked training data to improve model responses; delivered concise, pedagogical feedback.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    {Politecnico di Milano, \textnormal{\textit{Peer Tutor} | Milan, Italy}} % Job title
    {Jan 2022 – Sep 2024} % Date (s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted students at Politecnico di Milano with Foundations of Computer Science and Geometry and Linear Algebra exam preparation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    {Skyward Experimental Rocketry, \textnormal{\textit{Logistics Department Member} | Milan, Italy}} % Job title
    {Sep 2022 – Oct 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Built and managed partner relationships to support logistics operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventrynew
    {A.S.D. Vastogirardi, \textnormal{\textit{Match Analyst U19 National League} | Vastogirardi, Italy}} % Organisation
    {Aug 2019 – Jun 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Analyzed matches to identify team strengths and improvement areas.}
        \item {Prepared training sessions to address findings and improve results.}
        \item {Supported the head coach in maintaining team morale and a high-performance environment.}
      \end{cvitems}
    }

\end{cventries2}
