%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{PROJECTS}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


%----------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {HPC Bio Docking Pipeline\textnormal{ | Personal project}} % Project
    {Jan 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Built an end-to-end virtual screening pipeline for SARS-CoV-2 Mpro (6LU7) using AutoDock Vina.}
        \item {Automated ligand generation from SMILES via OpenBabel and implemented MPI-based distributed docking.}
        \item {Aggregated and ranked affinities with ligand efficiency metrics; generated interactive NGLView HTML reports and CSV summaries.}
        \item {Packaged the workflow for SLURM and Docker execution.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AN2DL Challenge 2 - Histology Slide Classification\textnormal{ | Politecnico di Milano}} % Project
    {Jan 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Built a histology slide classification pipeline for four breast cancer subtypes (Luminal A/B, HER2+, Triple Negative).}
        \item {Implemented HSV-based quality control to filter stained/artifact slides and ROI-centric multi-scale tiling with OpenCV.}
        \item {Developed attention-based MIL with a ViT-S backbone (timm/PyTorch), slide-level aggregation, and leakage-safe splits by original slide.}
        \item {Advanced from baseline ResNet-18 to ROI+multi-scale and AttnMIL, achieving test F1 = 0.3898.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AN2DL Challenge 1 - Time-Series Pain Classification\textnormal{ | Politecnico di Milano}} % Project
    {Jan 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Designed a time-series pipeline to predict pain status from multi-sensor data with subject-level splits to avoid leakage.}
        \item {Engineered preprocessing: one-hot encoding, variance/correlation filtering, PCA by joint group, and sliding windows (size 25, stride 2).}
        \item {Trained RNN/LSTM/GRU models with AdamW, label smoothing, class-weighted loss, and grid search; used 5-fold CV ensembling.}
        \item {Achieved test F1 up to 0.9567 with the best LSTM ensemble.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Football Penalty Takers Analysis\textnormal{ | Personal project}} % Project
    {Sep 2024 – Mar 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Developed a full-stack analytics platform to study penalty takers in Serie C, Group B (2024/25 season).}
        \item {Built the backend in Python with Flask, using Pandas for data processing and OpenPyXL for automated Excel report generation.}
        \item {Created HTML pages with Jinja2 templates, styled with CSS and enhanced with JavaScript for interactive visualization.}
        \item {Delivered an end-to-end workflow for data collection, analysis, visualization, and export, deployed on a personal website.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Project – Color to Grayscale Conversion\textnormal{ | Politecnico di Milano}} % Project
    {Jun 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a Google Test suite to validate grayscale conversion algorithms with property and robustness tests.}
        \item {Built CI/CD with GitHub Actions to automate build, test, and deployment.}
        \item {Containerized with Singularity and automated deployment to the Galileo100 HPC cluster via SLURM.}
        \item {Collaborated in a 4-person team, focusing on deployment automation and reliable container execution.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Parallel Computing Challenge\textnormal{ | Politecnico di Milano}} % Project
    {Nov 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented serial and multi-threaded merge sort in C++, evaluating scalability across input sizes and cutoff thresholds.}
        \item {Built a reproducible benchmarking pipeline producing CSV timing datasets and 2D/3D visualizations using Python and Gnuplot.}
        \item {Analyzed speedup and efficiency trade-offs between parallel and serial runs; summarized findings in a technical report.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NLA Challenge – Image Processing\textnormal{ | Politecnico di Milano}} % Project
    {Oct 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented an image-processing pipeline in C/C++ with discrete operators for edge detection, smoothing, and sharpening, with reproducible builds via Makefile.}
        \item {Handled image I/O and exported intermediate data in \texttt{.mtx} format for matrix-level inspection.}
        \item {Produced PNG artifacts and histograms to study noise/contrast effects and the behavior of discrete filters on real inputs.}
        \item {Built C routines and shell tooling to construct and analyze \(\mathbf{A}^\top\mathbf{A}\), computing spectral properties and validating results on real inputs.}
        \item {Integrated the LIS (Library of Iterative Solvers) for iterative methods on sparse matrices; managed \texttt{.mtx} datasets and produced plots for clean vs. noisy scenarios.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering\textnormal{ | Politecnico di Milano}} % Project
    {Jun 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Implemented the board game Codex Naturalis (Cranio Creations) in Java.}
        \item {Implemented a client/server protocol to support distributed multiplayer gameplay.}
        \item {Applied design patterns across the architecture and codebase.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Logical Networks\textnormal{ | Politecnico di Milano}} % Project
    {Mar 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Implemented a VHDL state machine to verify the credibility of data stored in memory.}
        \item {Validated functional correctness against course specifications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Introduction to Finite Elements and Algorithms\textnormal{ | Delft University, \textit{Athens Programme}}} % Project
    {Nov 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Implemented a finite element method problem using Julia.}
        \item {Analyzed the computational cost of linear system solvers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Algorithms and Data Structures\textnormal{ | Politecnico di Milano}} % Project
    {Sep 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Implemented management software in C to manage a highway and the electric vehicles used to traverse it.}
        \item {Analyzed the computational complexity of core operations.}
      \end{cvitems}
    }
\end{cventries}
